Asymptotic Validity of a Fully Sequential Elimination Procedure for Indifference-Zone Ranking and Selection with Tight Bounds on Probability of Correct Selection

### 2015-04-17 paper/paper_version2.tex
04/17/15

\[
\mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
\]
and the resulting expresion is

@@

The last part of our proof is to observe that (1) $\mathcal{C}\left(\delta,\cdot\right)$
converges to a multivariate Brownian motion $W$ as $\delta$ goes
to 0; (2) the function $f$ has a continuity property that causes
\[
f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)\Rightarrow g\left(W\right)
\]
where g is the selection decision from applying the BIZ procedure
in continuous time; and (3) the BIZ procedure satsifies the IZ guarantee
when applied in continuous time.

>>>>

\[
\mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
\]
and the resulting expression is

@@

The last part of our proof is to observe that (1) $\mathcal{C}\left(\delta,\cdot\right)$
converges to a multivariate Brownian motion $W$ as $\delta$ goes
to 0; (2) the function $f$ has a continuity property that causes
\[
f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)\Rightarrow g\left(W\right)
\]
where g is the selection decision from applying the BIZ procedure
in continuous time; and (3) the BIZ procedure satisfies the IZ guarantee
when applied in continuous time.
